### 2011-12-02 plos_template.tex
started writing the results

Since 2006 there are different companies like 23andMe, deCODEme or FamilyTreeDNA on the market which offer Direct-To-Consumer genetic testing. Those companies use DNA micro arrays to screen for around 1 million SNPs which are spread over the human genome. In return customers get an analysis of the results, as well as a raw file that includes the SNP-IDs and their respective allele for the customer. In 2011 23andMe alone had over 100.000 customers (http://spittoon.23andme.com/2011/06/15/23andme-2011-state-of-the-database-address/) and the company also recognizes the potential to do GWAS with that amount of data. They provide surveys to their customers that ask about traits and genetic diseases. With the consent of the customer those data will then be used for association studies. 23andMe published 3(?) articles in 2011 in which they replicate known findings but also find new associations for Parkinson's Disease. By activating their customer base they achieved to have over 30.000 individuals enrolled in those association studies.

@@

\subsection*{Subsection 1}

\subsection*{Subsection 2}

>>>>

Since 2006 there are different companies like 23andMe, deCODEme or FamilyTreeDNA on the market which offer Direct-To-Consumer (DTC) genetic testing. Those companies use DNA micro arrays to screen for around 1 million SNPs which are spread over the human genome. In return customers get an analysis of the results, as well as a raw file that includes the SNP-IDs and their respective allele for the customer. In 2011 23andMe alone had over 100.000 customers (http://spittoon.23andme.com/2011/06/15/23andme-2011-state-of-the-database-address/) and the company also recognizes the potential to do GWAS with that amount of data. They provide surveys to their customers that ask about traits and genetic diseases. With the consent of the customer those data will then be used for association studies. 23andMe published 3(?) articles in 2011 in which they replicate known findings but also find new associations for Parkinson's Disease. By activating their customer base they achieved to have over 30.000 individuals enrolled in those association studies.

@@

\subsection*{Survey on Sharing Genetic Information}
229 people, 169 with a self-reported chromosomal sex of XY, 59 with a self-reported chromosomal sex of XX, participated in the survey. The mean age of the participants is 33 and over 80 \% reported their ethnicity as caucasian. 40 \% of the participants are already customer of at least one DTC genetic testing company and further 30 \% of them plan to become one in the future. 30 \% don't plan to become a DTC customer. 
\subsection*{Subsection 2}
